TODO: A Survey of StarCraft AI Techniques

### 2013-02-23 survey.tex
updated text CIG 2012

@@

\begin{table*}[t!]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:cig-first-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
A1 & 0 &	 40 &	 UAlbertaBot & 82.5\% \\
A2 & 1 &  	 40 &	 Skynet	  &  77.5\% \\
A3 & 2 &	 40 &	 AIUR	  &  60.0\% \\
A4 & 1 &	 40 &	 Nova	  &  20.0\% \\
A5 & 0 &	 40 &	 LSAI	  &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
B1 & 12 &	 40 &	 Xelnaga &	 62.5\%\\
B2 & 3 &   40 &	 BroodwarBotQ  &  57.5\%\\
B3 & 0 &	 40 &	 BTHAI	  &  57.5\%\\
B4 & 17 &	 40 &	 Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &	 40 &	 EvoBot	  &  30.0\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

@@

@@

The final round was played in a similar mode as each of the
first round brackets,
using another set of 5 previously unknown maps:
\emph{iCCup lost temple 2.4}, \emph{iCCup rush hour 3.1},
\emph{iCCup swordinthemoon 2.1}, \emph{iCCup yellow 1.1},
and \emph{La\_Mancha 1.1}. 
Letting each pairing play on each map twice again with
switching starting positions resulted in 30 games per bot.
The final results are displayed in table~\ref{tab:cig-final-round},
indicating Skynet as winner and UAlbertaBot as runner-up, being
almost equally strong, and the two other bots as clearly inferior.

\begin{table}[t!]
\caption{Results of the CIG 2011 final round.}
\label{tab:cig-final-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
Position & crashes & games & bot	& win\%\\ \hline
1 & 0 &  30 &	 Skynet	  		&  86.7\%\\
2 & 0 &	 30 &	 UAlbertaBot 	&  73.3\%\\
3 & 3 &	 30 &	 Xelnaga  		&  36.7\%\\
4 & 2 &	 30 &	 BroodwarBotQ  	&  3.3\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table}

For CIG 2012, the AIIDE tournament software was employed,
leading to a total of $4050$ games played in $90$ rounds
of round robin. As 6 different maps were used, this means
that each bot played every other on every map 15 times.

>>>>

\begin{table*}[t]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:cig-first-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
A1 & 0 &	 40 &	 UAlbertaBot & 82.5\% \\
A2 & 1 &  	 40 &	 Skynet	  &  77.5\% \\
A3 & 2 &	 40 &	 AIUR	  &  60.0\% \\
A4 & 1 &	 40 &	 Nova	  &  20.0\% \\
A5 & 0 &	 40 &	 LSAI	  &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
B1 & 12 &	 40 &	 Xelnaga &	 62.5\%\\
B2 & 3 &   40 &	 BroodwarBotQ  &  57.5\%\\
B3 & 0 &	 40 &	 BTHAI	  &  57.5\%\\
B4 & 17 &	 40 &	 Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &	 40 &	 EvoBot	  &  30.0\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

\begin{table}[b]
\caption{Results of the CIG 2011 final round.}
\label{tab:cig-final-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
Position & crashes & games & bot	& win\%\\ \hline
1 & 0 &  30 &	 Skynet	  		&  86.7\%\\
2 & 0 &	 30 &	 UAlbertaBot 	&  73.3\%\\
3 & 3 &	 30 &	 Xelnaga  		&  36.7\%\\
4 & 2 &	 30 &	 BroodwarBotQ  	&  3.3\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table}

@@

\begin{figure}[t]
	%\vspace*{-1ex}
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/cig2012-ResultsRound90.pdf}
	%\vspace*{-1ex}
    \caption{Evolution of the win percentage of each bot participating in the
CIG 2012 competition}
    \label{fig:cig2012-results}
\end{figure}

\begin{table}[b]
\caption{Results of the CIG 2012 competition.}
\label{tab:cig2012}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|}
\hline
Position & bot & win \% \\ \hline
1 & Skynet & 78.3\% \\
2 & UAlbertaBot & 65.2\% \\
3 & AIUR & 60.4\% \\
4 & Adjutant & 58.6\% \\
5 & Nova & 52.4\% \\ \hline
\end{tabular}
\end{center}
\end{small}
\end{table}

@@

\begin{figure*}[t]
	%\vspace*{-2ex}
    \centering
    \includegraphics[width=0.34\textwidth]{figures/vstable3.pdf}
    \includegraphics[width=0.3\textwidth]{figures/vstable6.pdf}
    \includegraphics[width=0.3\textwidth]{figures/vstable.pdf}
	%\vspace*{-4ex}
    \caption{Win percentages of CIG 2012 competition, from left
    to right: 3-player maps only, 6-player maps only, all maps.
    Read from line to column, bot in row wins given fraction of
    games against bot in column. For some bots, we find interesting
    differences, e.g. Xelnaga gets worse on 6-player maps, UAlbertaBot
    gets better. Only Xelnaga can reliably beat Skynet, but only on 
    3-player maps}
    \label{fig:cig2012-mapresults}
\end{figure*}

@@

The final round was played in a similar mode as each of the
first round brackets,
using another set of 5 previously unknown maps:
\emph{iCCup lost temple 2.4}, \emph{iCCup rush hour 3.1},
\emph{iCCup swordinthemoon 2.1}, \emph{iCCup yellow 1.1},
and \emph{La\_Mancha 1.1}. 
Letting each pairing play on each map twice again with
switching starting positions resulted in 30 games per bot.
The final results are displayed in table~\ref{tab:cig-final-round},
indicating Skynet as winner and UAlbertaBot as runner-up, being
almost equally strong, and the two other bots as clearly inferior.
The competition setup, documentation and results can be found
in\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/starcraft-cig2011}}.

For CIG 2012, the AIIDE tournament software was employed,
leading to a total of $4050$ games played in $90$ rounds
of round robin. As 6 different maps were used, this means
that each bot played every other on every map 15 times. 
As in the AIIDE competition, writing to and reading from
a bot specific directory was enabled, however, due to 
technical reasons, this feature was constrained to the
computer (of 6) the game was actually run on. We can 
therefore assume that this feature was of minor use for
the CIG competition. The only other difference to the
AIIDE competition was that the used maps were not 
made available to the competitors in advance.

These maps came in two flavors, namely 3 3-player maps:
\emph{Athena-II}, \emph{Neo Moon Glaive}, \emph{Tears of the Moon},
and 3 6-player maps:
\emph{Legacy}, \emph{River of Light}, and 
\emph{The Huntress 1.1}. 
We shall note that some bots consistently crashed on one
of the originally considered maps which has thus been replaced.
This is surprising as all maps are well known league play maps
or have been provided with the StarCraft Broodwar distribution
itself.

\ref{tab:cig2012}

\ref{fig:cig2012-results}
\ref{fig:cig2012-mapresults}

map ‘size‘ has an effect!
 Nova against BBQ: good on 6-player, bad on 3-player
 SCAIL and Adjutant better on 6-player, BBQ worse on 	6-player
 UAlbertaBot better on 6-player (due to scouting?)
 Nova consistently good against UAlbertaBot
 Xelnaga only bot to beat Skynet, but only on 3-player 	maps

Here are the 2 replays shown in the presentation: Xelnaga surprising Skynet with a targetted DTS attack on its probes, and Nova successfully luring UAlbertaBot's probes into its own base.

things (many) bots can‘t do:
 handle islands
 play zerg
 play maps of different sizes (!!!)
 play against random race
 finish off beaten opponent
 adapt to opponent strategy
 cooperate (no teamplay)

Setup and results for the CIG 2012 competition are 
here\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/starcraft-cig2012}}.
